### 2017-03-06 paper/oopsla17-submission/learning.tex
more features

We choose to model a program as a \emph{set} of feature vectors, where
each element corresponds a sub-expression in the program. We group the
features into four categories.

@@

\paragraph{Typing features}

>>>>

We choose to model a program as a \emph{set} of feature vectors, where
each element corresponds a sub-expression in the program. We group the
features into the following categories.

@@

\paragraph{Typing features}
A natural way of summarizing the context in which an expression occurs
is with \emph{types}.
%
A difficulty that arises here is that, due to the parametric type
constructors $\tfun{\cdot}{\cdot}$, $\tprod{\cdot}{\cdot}$, and
$\tlist{\cdot}$, there is an \emph{infinite} set of possible types ---
but we must have a \emph{finite} set of features.
%
Thus, we add features for each type \emph{constructor} that describe
whether a given type \emph{mentions} the type constructor.
%
For example, the type $\tint$ would only enable the $\tint$ feature,
while the type $\tfun{\tint}{\tbool}$ would enable the
$\tfun{\cdot}{\cdot}$, $\tint$, and $\tbool$ features.
%
We add these features for parent and child expressions to summarize the
context, but also for the current expression, as the type of an
expression is not always clear \emph{syntactically} (\eg for variables
and applications).
\ES{note the possibility of traversal bias from typing features}

\paragraph{Type error slice}
Finally, we would like the model to be able to distinguish between
changes that could fix the error, and changes that
\emph{cannot possibly} fix the error.
%
Thus, we compute a minimal type error \emph{slice} for the program
(\ie the set of expressions that contribute to the error), and add a
feature that is enabled \emph{iff} an expression is part of the slice.
%
If the program contains multiple type errors, we will compute a minimal
slice for each error.
